Chapter 4: Binocular combination in the Autonomic Nervous System

### 2024-01-12 manuscript.Rmd
Modified command to download individual summary.RData files as it was not working properly. Now works as it should.

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',600+participant,'summaryLum.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',600+participant,'summaryLum.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',500+participant,'summaryMel.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',500+participant,'summaryMel.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',700+participant,'summaryLM.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',700+participant,'summaryLM.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',300+participant,'summaryS.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',300+participant,'summaryS.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

>>>>

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',600+participant,'_summaryLum.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',600+participant,'_summaryLum.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',500+participant,'_summaryMel.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',500+participant,'_summaryMel.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',700+participant,'_summaryLM.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',700+participant,'_summaryLM.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',300+participant,'_summaryS.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',300+participant,'_summaryS.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}
